---
title: "Behaviors EDA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries

```{r}
library(tidyverse)
library(arrow)
```


Obtain implicit positive and negative articles from `history` and `impressions` columns:

```{r}
history <- behaviors_train %>%
  select(user_id, time, history) %>%
  separate_rows(history) %>%
  rename(article = history) %>%
  add_column(label = 1L) 
  
impressions <- behaviors_train %>%
  select(user_id, time, impressions) %>%
  separate_rows(impressions, sep = " ") %>%
  separate(impressions, into = c("article", "label")) %>%
  mutate(label = as.integer(label))
```


Goal: Obtain positive and negative article interactions for each user (positive if they clicked on the article, negative
if the article appeared as an impression and they did not click on it.

If a user-article pair appears twice in the data, we'll choose label=1 over label=0 (since they clicked on it at some point). Also, for duplicated user-article
pairs with the same label, chose the most recent.

Warning: The following is really slow! 

```{r}
interactions <- bind_rows(history, impressions) %>%
  mutate(time = mdy_hms(time)) %>%
  group_by(user_id, article, label) %>%
  slice_max(order_by = time) %>%          # Pick most recent for each label, user, article
  ungroup() %>%
  group_by(user_id, article) %>%
  slice_max(order_by = label)             # Pick label=1 over label=0 for duplicated user-article pairs

```

