---
title: "MIND"
output: html_document
---

See https://github.com/msnews/msnews.github.io/blob/master/assets/doc/introduction.md


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries:

```{r}
library(tidyverse)
library(reticulate)
```

Behavior files provide user impressions and click history:

* Impression ID. The ID of an impression.
* User ID. The anonymous ID of a user.
* Time. The impression time with format "MM/DD/YYYY HH:MM:SS AM/PM".
* History. The news click history (ID list of clicked news) of this user before this impression. The clicked news articles are ordered by time.
* Impressions. List of news displayed in this impression and user's click behaviors on them (1 for click and 0 for non-click). The orders of news in a impressions have been shuffled.

```{r}
col_names <- c("impression_id", "user_id", "time", "history", "impressions")
behaviors_train <- read_tsv(file = "/data/MINDsmall/train/behaviors.tsv", col_names = col_names)
behaviors_val <- read_tsv(file = "/data/MINDsmall/val/behaviors.tsv", col_names = col_names)
```

News files contain information about each news article:

* News ID
* Category
* SubCategory
* Title
* Abstract
* URL
* Title Entities (entities contained in the title of this news)
* Abstract Entities (entities contained in the abstract of this news)

Note: R's `read_tsv` had some trouble reading the news dataset, so we'll use python pandas.

```{python}
import pandas as pd
news_train = pd.read_csv("/data/MINDsmall/train/news.tsv", sep="\t", header=None )
news_val = pd.read_csv("/data/MINDsmall/val/news.tsv", sep="\t", header=None )
```

```{r}
news_train <- py$news_train
news_val <- py$news_val
col_names <- c("news_id", "category", "subc-ategory", "title", "abstract", "url", "title_entities", "abstract_entities")
colnames(news_train) <- col_names
colnames(news_val) <- col_names
#View(news)
```

Each record of the embedding files contains an id and a 100 dimensional embedding. Embeddings are provided for entities and relations learned from the subgraph (from WikiData knowledge graph).

```{r}
col_names <- c("id", sapply(1:100, function(x){sprintf("d%d",x)}))

entity_embedding_train <- read_tsv(file = "/data/MINDsmall/train/entity_embedding.vec") %>% select(-X102)
colnames(entity_embedding_train) <- col_names

entity_embedding_val <- read_tsv(file = "/data/MINDsmall/val/entity_embedding.vec") %>% select(-X102)
colnames(entity_embedding_val) <- col_names

relation_embedding_train <- read_tsv(file = "/data/MINDsmall/train/relation_embedding.vec")
colnames(relation_embedding_train) <- col_names

relation_embedding_val <- read_tsv(file = "/data/MINDsmall/val/relation_embedding.vec")
colnames(relation_embedding_val) <- col_names
```

